\documentclass[11pt]{sdm}
\usepackage{graphicx}
\usepackage[style=alphabetic,sorting=nyt, backend=biber]{biblatex}
\addbibresource{Biblio.bib}

%numeroter les pages
\pagestyle{plain}

\title{SCARE for Hardware SPN}
\author{First\_Name \textsc{Name}}
\supervisorOne{First\_Name \textsc{Name} of your first supervisor}
\supervisorTwo{First\_Name \textsc{Name} of your second supervisor}
\team{Name of the team in which you are doing your internship}
%One of:
% ens-Rennes  esir    insa-rennes   rennes1  
% enssat    logoUbs   tsupelec
%here rennes1 for example
\school{supelec}


% the domain should be one or two of:
% Technology for Human Learning 
% Artificial Intelligence 
% Computer Arithmetic
% Hardware Architecture
% Automatic Control Engineering
% Bioinformatics 
% Biotechnology
% Computational Complexity 
% Computational Engineering, Finance, and Science
% Computational Geometry 
% Computation and Language 
% Cryptography and Security 
% Computer Vision and Pattern Recognition
% Computers and Society 
% Databases 
% Distributed, Parallel, and Cluster Computing 
% Digital Libraries
% Discrete Mathematics 
% Data Structures and Algorithms 
% Embedded Systems 
% Emerging Technologies 
% Formal Languages and Automata Theory 
% General Literature 
% Graphics 
% Computer Science and Game Theory 
% Human-Computer Interaction 
% Computer Aided Engineering 
% Medical Imaging 
% Information Retrieval 
% Information Theory 
% Ubiquitous Computing 
% Machine Learning
% Logic in Computer Science 
% Multiagent Systems 
% Mobile Computing
% Multimedia
% Modeling and Simulation 
% Mathematical Software 
% Numerical Analysis 
% Neural and Evolutionary Computing 
% Networking and Internet Architecture 
% Operating Systems 
% Performance 
% Programming Languages 
% Robotics 
% Operations Research
% Symbolic Computation 
% Sound
% Software Engineering 
% Social and Information Networks 
% Systems and Control 
% Image Processing 
% Signal and Image Processing 
% Document and Text Processing
% Web
\domain{Domain: Cryptography and Security}

%write your abstract here
\abstract{write your abstract here}



\begin{document}
\maketitle

%*****************************************************************%

\section*{Introduction}

Here start your document - Should be 15 pages long \\

Following Kerchoffs' principle, the security of a cryptographic device shall not rely on the secrecy of its mechanisms \cite{Kerckhoffs_1883}.
However in some specific contexts, having a secret implementation can add a layer of security, by increasing the practical difficulty of the attack.

\section{State of the art of Side Channel Attacks on SPNs}

\subsection{SPNs, Feistel schemes, DES and AES}

Feistel scheme, DES

\cite{Standards2001}

\subsection{Side Channel Analysis classic attacks}

SPA, DPA, CPA explanation (ref papers ?)

\cite{Chari_Rao_Rohatgi_2003} presents template attacks, "the strongest form of side channel attack possible in an information theoretic sense".

\cite{Prouff_Rivain_1970} presents the theory of Mutual Information Attacks (MIA) in side channels.

Machine Learning is very popular right now.

\section{SCARE attacks}

\subsection{SCARE attacks on non AES ciphers}

\cite{Novak_2003} presents a side-channel attack on substitution blocks with a demonstration on a SIM card using COMP-128 cipher.

\cite{Daudigny_Ledig_Muller_Valette_2005} presents a SCARE attack on DES and propose new methods to exploit the power measurement information.

\cite{Guilley_Sauvage_Micolod_Réal_Valette_2010} presents two SCARE attacks on the parameters of a LFSR and DES.

\subsection{SCARE attacks on AES-like ciphers}

\cite{Tiessen_Knudsen_Kölbl_Lauridsen_2015} presents an integral cryptanalysis of an AES with a secret S-box and less rounds. It is not a SCA but is still closely related to our subject.

\cite{Rivain_Roche_2013} presents a generic SCARE attack against a wide class of SPN block ciphers.

FIRE (injection fault attempts) and SCARE attacks to recover the full set of secret parameters of an AES-like software implementation, even with masking and shuffling \cite{Clavier_Isorez_Marion_Wurcker_2015}.

\section{Application to hardware implementations}

\subsection{Differences between software and hardware cryptographic implementations}

\begin{itemize}
    \item The sequential execution becomes parallel
    \item There is even more noise
    \item SCA leaks cannot be determined as precisely
    \item It takes more time to implement, develop and attack
\end{itemize}

\subsection{Attacks on hardware design}

\cite{Réal_Dubois_Guilloux_Valette_Drissi_2008} presents a SCARE attack on a general Feistel scheme with an hardware design.

SAKURA board reference

SCA attacks on FPGAs (\cite{Peeters_Standaert_Donckers_Quisquater_2005} or more relevantly \cite{Standaert_Ors_Preneel_2004} or something more recent)

\section{Conclusion}

\section*{References}

\printbibliography

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: